### 2017-01-09 slides/figures/vae_conceptual.tex.preview.tex
synced

\documentclass{standalone}

\usepackage{pgfplots}
\pgfplotsset{compat=1.14}
\usetikzlibrary{fit,backgrounds}

\usetikzlibrary{positioning, arrows.meta, calc, shapes.misc}

@@

% output / reconstruction
\node[gb] (output) at ($(input) + (3.0cm,0.0cm)$) {$\tilde x$};
\node[fill=black!20] (lbl_rec) at ($(output) + (0,-1cm)$) {Reconstruction};

@@

    %\begin{pgfonlayer}{background}

% draw plot for normal dist
\begin{axis}[
  no markers,
  domain=0:6,
  samples=100,
  ytick=\empty,
  width=3.5cm,
  xtick=\empty,
  xlabel={$(\mu,\sigma)$},
  at={($(input) + (-0.95cm,4.5cm)$)}
  ]
  \addplot [thick,cyan!50!black, domain=0:6] {gauss(3,1)};
  \node[] (left_bot) at (axis cs:0.0,-0.15) {};
  \node[] (left_top_aux) at (axis cs:0.0,0.2) {};
\end{axis}

  \node [above right=of left_top_aux] (left_top) {Latent space};

    %\end{pgfonlayer}
\begin{scope}[on background layer]
  \node (outer) [dashed,draw,fill=blue!10,fit=(left_bot) (left_top) (lbl_lat)] {};
\end{scope}

% input -> latent
\draw[arr] (input) -- node[label=left:$q_\phi(z|x)$] {}($(input) + (0.0cm,3.8cm)$) {};

@@

\end{tikzpicture}
\end{document}

>>>>

\documentclass{standalone}
\usepackage{pgfplots}
\usetikzlibrary{fit,backgrounds}

\pgfplotsset{compat=1.14}
\usetikzlibrary{positioning, arrows.meta, calc, shapes.misc}

@@

% output / reconstruction
\node[gb] (output) at ($(input) + (3.0cm,0.0cm)$) {$\tilde x$};
%\node[fill=black!20] (lbl_rec) at ($(output) + (0,1cm)$) {Reconstruction};

@@

%\begin{scope}
    %\begin{pgfonlayer}{background}
%\begin{scope}[on background layer]
%  \node (outer) [draw,fill=blue,fit=($(input) + (-0.95cm,4.5cm) (output)] {};%
%\end{scope}
%\node (ax)  [above of=input,label=above:$s\le 3$] {};

% draw plot for normal dist
\begin{axis}[
  no markers,
  domain=0:6,
  samples=100,
  ytick=\empty,
  xtick=\empty,
  xlabel={$(\mu,\sigma)$},
  width=3.5cm,
  at={($(input) + (-0.95cm,4.5cm)$)}
  ]
  \addplot [very thick,cyan!50!black, domain=0:6] {gauss(3,1)};

\end{axis}
    %\end{pgfonlayer}

% input -> latent
\draw[arr] (input) -- node[label=left:$q_\phi(z|x)$] {}($(input) + (0.0cm,4.0cm)$) {};

@@

\usetikzlibrary{calc}
\pgftransformreset
\node[inner sep=0pt,outer sep=0pt,minimum size=0pt,line width=0pt,text width=0pt,text height=0pt] at (current bounding box) {};
%add border to avoid cropping by pdflibnet
\foreach \border in {0.1}
  \useasboundingbox (current bounding box.south west)+(-\border,-\border) rectangle (current bounding box.north east)+(\border,\border);
\newwrite\metadatafile
\immediate\openout\metadatafile=\jobname_BB.txt
\path
  let
    \p1=(current bounding box.south west),
    \p2=(current bounding box.north east)
  in
  node[inner sep=0pt,outer sep=0pt,minimum size=0pt,line width=0pt,text width=0pt,text height=0pt,draw=white] at (current bounding box) {
\immediate\write\metadatafile{\p1,\p2}
};
\immediate\closeout\metadatafile
\end{tikzpicture}
\end{document}
